\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2013-05-16 doc/sw-system.tex
Updated information content by agent, updated plot and startup config

% This is incorrect, so for the moment commenting it out
%Indeed, the information content of each classification can be estimated by an
%agent before the next classification is made, just from its confusion matrix.
%We define the expected contributed information per classification, as
%\be
%  \langle I_k \rangle = \frac{1}{2} 
%                        \sum_{i} \left( \mathcal{M}^k_{i}  
%              + \mathcal{M}^k_{i}\cdot\log_2{\mathcal{M}^k_i} \right),
%  \label{eq:app:info}
%\ee
%where $i$ runs over all 4 elements of the confusion matrix 
%$\mathcal{M}^k_i$, and $\langle I_k \rangle$ is measured in ``bits.'' 
%The second term in the sum is recognisable as a
%negative entropy, while the first term and the factor of 1/2
%account for the way the confusion matrix encodes the results for the
%classification of two types of subject, and that the probabilities
%associated with each type are normalised. \Eref{eq:app:info} gives the
%required result, that 
%both the hypothetical {\it perfect} and
%{\it obtuse} classifiers contribute 
%1 bit of information each, per classification. 
%
%In fact, the only classifier that contributes the minimum information per
%classification, zero bits, is the {\it random} classifier, whose agent's
%confusion matrix elements are all 0.5.

>>>>

Indeed, the information content of each classification can be estimated by an
agent before the next classification is made, just from its confusion matrix.
We define the expected contributed information per classification, as
\be
  \langle I_k \rangle = \frac{1}{2} 
    \left(
    \mathcal{M}^k_{d}\cdot\log_2{\mathcal{M}^k_d} +  \mathcal{M}^k_{o}\cdot\log_2{\mathcal{M}^k_o} \right),
  \label{eq:app:info}
\ee
where $\mathcal{M}^k_d$ and $\mathcal{M}^k_o$ is the sum of the diagonal and
the off-diagonal elements of the confusion matrix and $\langle I_k \rangle$ is
measured in ``bits.'' The factor of 1/2 accounts for the way the confusion
matrix encodes the results for the classification, and
that the probabilities associated with each type are normalised.
\Eref{eq:app:info} gives the required result, that both the hypothetical {\it
perfect} and {\it obtuse} classifiers contribute 1 bit of information each, per
classification.

In fact, the only classifier that contributes the minimum information per
classification, zero bits, is the {\it random} classifier, whose agent's
confusion matrix elements are all 0.5.
